Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and interpolation-extrapolation capacity validation

### 2022-11-10 Article.tex
Update text of Comparison section

The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition ($6$ strain rates and $5$ temperatures) is presented in Figure \ref{fig:rawData}.
\OP{It is necessary to give indications concerning the structure of the data: how many points, what amplitude of deformation,...}\textcolor{red}{almost all data are around 21030 or less than and the ammplitude of deformation is between $0.7$ and $0.85$.
We have decided to limit the identification up to $0.7$ because for strain rates $2$ and $5$, stresses are note good}.
The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
It should be noted that the strain also influences the flow stress.
Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
For the highest strain rates ($1.0~\ps$, $2.0~\ps$, and $5.0~\ps$), the flow stress increases throughout the test.
One reason for the slight increase in stress at low strain rates when the strain is large is due to friction between the sample and the anvil during the test.
For low strain rates, the effect of lubrication decreases over time and thus friction increases.
This results in a progressive increase of the flow stress.

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]{Figures/rawData}
\caption{Flow stress-strain curves of AISI P20 alloy at various temperatures and strain rates.}
\label{fig:rawData}
\end{figure}

To explain the overall flow stress behavior observed in this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRC) and Dynamic Recrystallization (DRX).
At the beginning of the deformation of the sample in compression, the amount of dislocations increases and they begin to move within the material, which leads to a rapid increase in stress (strain hardening phenomenon).
As the strain continues to increase, many dislocations are in motion, leading to a stress relaxation phenomenon, generally known as DRC.
This DRC mechanism contributes to the decrease in the number of dislocations due to their combination with another dislocation or due to their integration into a grain boundary.
Some of these dislocations reorganize and then form sub-grains within the initial grains of the material.
The combination of these dislocations moderates the increase in the number of dislocations related to work hardening and thus controls the amount of strain energy stored in the material, which influences the increase in flow stress.
The dynamic recrystallization concerns the germination of new grains, at the borders or inside the initial grains.
These two phenomena explain the different shapes of the flow stress curves observed for this alloy.
As an example, Figure \ref{fig:Micrography} show the microstructures of AISI P20 held during $5$~min at $1260\celsius$ before and after the compression phase.
As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample \textcolor{red}{held for $5$ minutes at $1260^\circ$C and rapidely cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001\ \text{s}^{-1}$}.
\OP{What are the temperature and strain rate related with this micrography}
From the results reported in Figure \ref{fig:rawData}, the identification of the parameters of the six flow laws proposed in this work will be presented in the next section in order to predict the behavior of the material in any test condition.

@@

The procedure used for the determination of the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{He-2013}.
This method allows obtaining one after the other the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate and reference temperature is $A=13.5143$~MPa.
For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, it is then possible to determine these two constants by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
Thus, here, $B=21.816$~MPa and $n=0.0746$.
Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering all the curves at $T=T_0$ then gives $C=0.3404$.
Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from the knowledge of the previous and gives $m=0.7057$.
All parameters of the Johnson-Cook model are reported in Table \ref{tab:JCparams}.

\begin{table}[h!]
\centering
\caption{Parameters' values of the Johnson-Cook flow law for the P20 steel.}
\begin{tabular}{ccccc}
\hline
$A~(\text{MPa})$ & $B~(\text{MPa})$ & $n$ & $C$ & $m$\\
$13.5143$&$21.816$&$0.0746$&$0.3404$&$0.7057$\\ \hline
\label{tab:JCparams}
\end{tabular}
\end{table}

The values predicted by the Johnson-Cook flow law (solid line) and the experimental values (dots) are compared in Figure \ref{fig:iCorrelationJC}.
The JC model is not able to describe the evolution of the flow stress of AISI P20 for all strain values, and the predicted stresses $\sigma^y$ show a monotonically decreasing trend for several values of the strain rates.
The discrepancy between the predicted and experimental values is large for low strains and sometimes acceptable for high strains.
As expected, the mathematical formulation of the Johnson-Cook flow law is unable to represent the stress drop at low strain rates, the JC model being only monotonically increasing with strain.
Since most of the parameters are identified at low strain rates ($A$, $B$ and $n$), this results in a very poor fit of the model to the experimental data.

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]{Figures/CompExp-JC-6}
\caption{Comparison between the experimental and predicted flow stresses by JC model.}
\label{fig:iCorrelationJC}
\end{figure}

@@

Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot\varepsilon=\mdot{\varepsilon}_0)$.
When the current strain rate $\mdot\varepsilon$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
\begin{equation}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
\end{equation}
Taking the logarithm of the previous relationship we have :
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
\end{equation}
By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
From the expression of $I_1$ we can write:
\begin{equation}
\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
\end{equation}
By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$.
The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively.
Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$.
Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$.
The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}.
It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates.
The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation.
For the MZA model, $\AARE=21.20~\%$ and $\RMSE=19.57~\text{MPa}$, this shows an overall worse performance than the JC model.
That is aspect of the limitations of that model as presented in \cite{TizeMha-2022}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
\begin{tabular}{ccccccc}
\hline
$C_1$ & $C_2$ & $C_3$ & $C_4$ & $C_5$ & $C_6$ & $n$\\
$13.5143$ & $21.2591$ & $4.7902\times 10^{-3}$ & $1.4895\times 10^{-4}$ & $0.1389$ & $1.495\times 10^{-4}$ & $0.0621$\\
\hline
\label{tab: MZAparameters}
\end{tabular}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExp-MZA-6}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:iCorrelationMZA}
\end{figure}

@@

In the present study, the best results were obtained by taking the model defined by only the first $7$ $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.\OP{See identification script for changes}
From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} has allowed to compute the parameters reported in Table \ref{tab:HSparameters}.

\begin{table}[h!]
\centering
\caption{Parameters' values of the Hansel-Spittel flow law for the P20 steel.}
\begin{tabular}{ccccc}
\hline
$A$ & $m_1$ & $m_2$ & $m_3$ & $m_4$\\
$5.954\times 10^{3}$ & $-3.3576\times10^{-3}$ & $0.2641$ & $-0.0868$ & $2.2688\times10^{-4}$\\\hline
& $m_5$ & $m_6$ & $m_7$ & $m_8$\\
& $-4.2163\times10^{-4}$ & $-0.0561$ & $2.264\times10^{-4}$ & $0$\\\hline
\label{tab:HSparameters}
\end{tabular}
\end{table}

The comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:iCorrelationHS} where the dots represent the experimental values and the solid lines are the values predicted by the Hansel-Spittel flow law.
For the HS model, $\AARE=7.75~\%$ and $\RMSE=3.80~\text{MPa}$.
It appears that this model as well as the previous ones do not predict well the experimental one and the difference is relatively important for all strain rates below $1.0~\ps$.
This shows that this model is not appropriate for the characterization of this alloy, in particular because of the strong non-linearity of the behavior for low values of the strain rate.
The DRX phenomena cannot be reproduced by this type of model.

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExp-HS-6}
\caption{Comparison between the experimental and predicted flow stresses by HS model}
\label{fig:iCorrelationHS}
\end{figure}

@@

The determination of the order $m$ of the polynomials defined by Equations (\ref{eq:ArA}-\ref{eq:Arn}) is defined according to the ability of the model to represent the non-linear dependence of the stress versus the strain and its generalization.
The values $\ln\!A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=1,2,3,\cdots,m$) are the coefficients of the polynomials to determine using a regression method.
Setting $m=9$ gives the best results and the corresponding parameters are reported in Table \ref{tab:ARparameters}.
\begin{table}[h!]
\centering
\caption{Parameters' values of the Arrhenius flow law for the P20 steel}
\begin{tabular}{llll}
\hline
\multicolumn{1}{c}{$\alpha_i$} & \multicolumn{1}{c}{$Q_i~(\times 10^{-6})$} & \multicolumn{1}{c}{$\ln\!A_i$} & \multicolumn{1}{c}{$n_i$}\\
\hline
$\alpha_0=0.0407$ & $Q_0=0.467$ & $A_0=35.8092$ & $n_0=4.8217$\\
$\alpha_1=-0.5167$ & $Q_1=-0.6517$ & $A_1=-58.822$ & $n_1=3.2814$\\
$\alpha_2=6.3912$ & $Q_2=7.6084$ & $A_2=740.3303$ & $n_2=71.5963$\\
$\alpha_3=-47.3364$ & $Q_3=-48.016$ & $A_3=-5.0493\times 10^{3}$ & $n_3=-1.9562\times 10^{3}$\\
$\alpha_4=220.0014$ & $Q_4=66.795$ & $A_4=1.1305\times 10^{4}$ & $n_4=1.4461\times 10^{4}$\\
$\alpha_5=-654.4553$ & $Q_5=468.8898$ & $A_5=2.022\times 10^{4}$ & $n_5=-5.431\times 10^{4}$\\
$\alpha_6=1.2421\times 10^{3}$ & $Q_6=-2.3032\times 10^{3}$ & $A_6=-1.5387\times 10^{5}$ & $n_6=1.1761\times 10^{5}$\\
$\alpha_7=-1.4523\times 10^{3}$ & $Q_7=4.3707\times 10^{3}$ & $A_7=3.1798\times 10^{5}$ & $n_7=-1.4882\times 10^{5}$\\
$\alpha_8=952.0619$ & $Q_8=-3.9394\times 10^{3}$ & $A_8=-2.9725\times 10^{5}$ & $n_8=1.0239\times 10^{5}$\\
$\alpha_9=-267.4994$ & $Q_9=1.397\times 10^{3}$ & $A_9=1.0759\times 10^{5}$ & $n_9=-2.9621\times 10^{4}$\\
\hline
\label{tab:ARparameters}
\end{tabular}
\end{table}
This modified form of the Arrhenius behavior law allows for accurate and reliable prediction over a wide range of temperatures and strain rates.
Equation (\ref{eq:ArStress}) is finally used to compute the flow stress $\sigma^y$ from the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$:
\begin{equation}
\sigma^y = \frac{1}{\alpha(\varepsilon)} \ln\left\{\left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{1}{n(\varepsilon)}} + \left[1 + \left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{2}{n(\varepsilon)}}\right]^{\frac{1}{2}}\right\}
\label{eq:ArStress}
\end{equation}

Figure \ref{fig:iCorrelationAR} shows the comparison of the values predicted by the Arrhenius model and the experimental values.
The difference between the experimental and predicted values is small.
But for the strain rate $\mdot\varepsilon = 0.01~\ps$ and for the two low temperature values, the AR model is not able to predict the softening.
For the AR model, $\AARE=3.56~\%$ and $\RMSE=2.18~\text{MPa}$.

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExp-AR-6}
\caption{Comparison between the experimental and predicted flow stresses by AR model}
\label{fig:iCorrelationAR}
\end{figure}

@@

The PTM model \cite{TizeMha-2022} is a generalized formulation of the MZA model presented in Section \ref{sec:MZA}.
When establishing its formulation, the main shortcomings of the MZA model were taken into account, in order to make the PTM model flexible for any type of material studied because there is no need for a limited number of parameters as in the MZA model.
Its construction is based on the use of polynomial functions as in the AR model.
Thus, the intrinsic functions of the model, of polynomial type, allow to adjust the model according to the degree selected for each of the 4 constituent polynomials, which provides a good fit for each function.
The equation describing the PTM model is therefore given by :
\begin{equation}
\label{eq:PTM-model}
\sigma^y = \left(\sum_{i=0}^{q}{A_i\varepsilon^{p^i}}\right) \exp\left[\left(\sum_{j=0}^{r}{B_j\varepsilon^{p^j}}\right)\left(T-T_0\right) + \left(\sum_{k=0}^{s}\left(\sum_{l=0}^{t}{C_k^l\varepsilon^{p^l}} \right)\left(T-T_0\right)^k \right)\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)\right]
\end{equation}
where $A_i, B_j, C_k^l$ are the parameters (Table \ref{tab:PTM-parameters}) of the model to be identified using the procedure proposed in  \cite{TizeMha-2022}.
Quantities $q$, $r$, $s$ and $t$ define the degree of the polynomials used to describe the behavior of the material.
The larger these quantities are, the more parameters need to be identified for the PTM model.
The determination of the parameters of this model are calculated thanks to the LMFIT Python library \cite{Newville-2016} and for more details about this model  we invite the reader to read our previous work \cite{TizeMha-2022}.
Thus all the parametrers of this model are calcuted with $q=5$, $r=5$, $s=1$ and $t=5$.

Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:iCorrelationPTM}.
The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$ the prediction in not quite good.
The deviation between the predicted values and the experimental values for other strain rates is relatively good.
For the PTM model, $\AARE=4.79~\%$ and $\RMSE=4.59~\text{MPa}$ this shows an overall worse performance than the AR model.

>>>>

The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition ($6$ strain rates and $5$ temperatures) is presented in Figure \ref{fig:RawData}.
\OP{It is necessary to give indications concerning the structure of the data: how many points, what amplitude of deformation,...}\textcolor{red}{almost all data are around 21030 or less than and the ammplitude of deformation is between $0.7$ and $0.85$.
We have decided to limit the identification up to $0.7$ because for strain rates $2$ and $5$, stresses are note good}.
The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
It should be noted that the strain also influences the flow stress.
Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
For the highest strain rates ($1.0~\ps$, $2.0~\ps$, and $5.0~\ps$), the flow stress increases throughout the test.
One reason for the slight increase in stress at low strain rates when the strain is large is due to friction between the sample and the anvil during the test.
For low strain rates, the effect of lubrication decreases over time and thus friction increases.
This results in a progressive increase of the flow stress.

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]{Figures/rawData}
\caption{Flow stress-strain curves of AISI P20 alloy at various temperatures and strain rates.}
\label{fig:RawData}
\end{figure}

To explain the overall flow stress behavior observed in this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRC) and Dynamic Recrystallization (DRX).
At the beginning of the deformation of the sample in compression, the amount of dislocations increases and they begin to move within the material, which leads to a rapid increase in stress (strain hardening phenomenon).
As the strain continues to increase, many dislocations are in motion, leading to a stress relaxation phenomenon, generally known as DRC.
This DRC mechanism contributes to the decrease in the number of dislocations due to their combination with another dislocation or due to their integration into a grain boundary.
Some of these dislocations reorganize and then form sub-grains within the initial grains of the material.
The combination of these dislocations moderates the increase in the number of dislocations related to work hardening and thus controls the amount of strain energy stored in the material, which influences the increase in flow stress.
The dynamic recrystallization concerns the germination of new grains, at the borders or inside the initial grains.
These two phenomena explain the different shapes of the flow stress curves observed for this alloy.
As an example, Figure \ref{fig:Micrography} show the microstructures of AISI P20 held during $5$~min at $1260\celsius$ before and after the compression phase.
As observed on the flow curves, it can be seen by comparing these two micrographs that recrystallization is almost complete for this temperature and strain rate within the sample \textcolor{red}{held for $5$ minutes at $1260^\circ$C and rapidely cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001\ \text{s}^{-1}$}.
\OP{What are the temperature and strain rate related with this micrography}
From the results reported in Figure \ref{fig:RawData}, the identification of the parameters of the six flow laws proposed in this work will be presented in the next section in order to predict the behavior of the material in any test condition.

@@

The procedure used for the determination of the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{He-2013}.
This method allows obtaining one after the other the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate and reference temperature is $A=13.5143$~MPa.
For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, it is then possible to determine these two constants by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
Thus, here, $B=21.816$~MPa and $n=0.0746$.
Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering all the curves at $T=T_0$ then gives $C=0.3404$.
Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from the knowledge of the previous and gives $m=0.7057$.
All parameters of the Johnson-Cook model are reported in Table \ref{tab:JC}.

\begin{table}[h!]
\centering
\caption{Parameters' values of the Johnson-Cook flow law for the P20 steel.}
\begin{tabular}{ccccc}
\hline
$A~(\text{MPa})$ & $B~(\text{MPa})$ & $n$ & $C$ & $m$\\
$13.5143$&$21.816$&$0.0746$&$0.3404$&$0.7057$\\ \hline
\label{tab:JC}
\end{tabular}
\end{table}

The values predicted by the Johnson-Cook flow law (solid line) and the experimental values (dots) are compared in Figure \ref{fig:CompExp-JC-6}.
The JC model is not able to describe the evolution of the flow stress of AISI P20 for all strain values, and the predicted stresses $\sigma^y$ show a monotonically decreasing trend for several values of the strain rates.
The discrepancy between the predicted and experimental values is large for low strains and sometimes acceptable for high strains.
As expected, the mathematical formulation of the Johnson-Cook flow law is unable to represent the stress drop at low strain rates, the JC model being only monotonically increasing with strain.
Since most of the parameters are identified at low strain rates ($A$, $B$ and $n$), this results in a very poor fit of the model to the experimental data.

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]{Figures/CompExp-JC-6}
\caption{Comparison between the experimental and predicted flow stresses by JC model.}
\label{fig:CompExp-JC-6}
\end{figure}

@@

Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot\varepsilon=\mdot{\varepsilon}_0)$.
When the current strain rate $\mdot\varepsilon$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
\begin{equation}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
\end{equation}
Taking the logarithm of the previous relationship we have :
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
\end{equation}
By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
From the expression of $I_1$ we can write:
\begin{equation}
\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
\end{equation}
By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$.
The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively.
Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$.
Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$.
The parameters of MZA model are given in the Table \ref{tab:MZA} while its prediction are shown in Figure \ref{fig:CompExp-MZA-6}.
It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates.
The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation.
For the MZA model, $\AARE=21.20~\%$ and $\RMSE=19.57~\text{MPa}$, this shows an overall worse performance than the JC model.
That is aspect of the limitations of that model as presented in \cite{TizeMha-2022}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
\begin{tabular}{ccccccc}
\hline
$C_1$ & $C_2$ & $C_3$ & $C_4$ & $C_5$ & $C_6$ & $n$\\
$13.5143$ & $21.2591$ & $4.7902\times 10^{-3}$ & $1.4895\times 10^{-4}$ & $0.1389$ & $1.495\times 10^{-4}$ & $0.0621$\\
\hline
\label{tab:MZA}
\end{tabular}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExp-MZA-6}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:CompExp-MZA-6}
\end{figure}

@@

In the present study, the best results were obtained by taking the model defined by only the first $7$ $m_i$ terms of the equation (\ref{eq:HS}), so that $m_8=0$.\OP{See identification script for changes}
From the experimental data obtained during the compression tests, an identification procedure based on the use of the LMFIT optimizer \cite{Newville-2016} has allowed to compute the parameters reported in Table \ref{tab:HS}.

\begin{table}[h!]
\centering
\caption{Parameters' values of the Hansel-Spittel flow law for the P20 steel.}
\begin{tabular}{ccccc}
\hline
$A$ & $m_1$ & $m_2$ & $m_3$ & $m_4$\\
$5.954\times 10^{3}$ & $-3.3576\times10^{-3}$ & $0.2641$ & $-0.0868$ & $2.2688\times10^{-4}$\\\hline
& $m_5$ & $m_6$ & $m_7$ & $m_8$\\
& $-4.2163\times10^{-4}$ & $-0.0561$ & $2.264\times10^{-4}$ & $0$\\\hline
\label{tab:HS}
\end{tabular}
\end{table}

The comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:CompExp-HS-6} where the dots represent the experimental values and the solid lines are the values predicted by the Hansel-Spittel flow law.
For the HS model, $\AARE=7.75~\%$ and $\RMSE=3.80~\text{MPa}$.
It appears that this model as well as the previous ones do not predict well the experimental one and the difference is relatively important for all strain rates below $1.0~\ps$.
This shows that this model is not appropriate for the characterization of this alloy, in particular because of the strong non-linearity of the behavior for low values of the strain rate.
The DRX phenomena cannot be reproduced by this type of model.

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExp-HS-6}
\caption{Comparison between the experimental and predicted flow stresses by HS model}
\label{fig:CompExp-HS-6}
\end{figure}

@@

The determination of the order $m$ of the polynomials defined by Equations (\ref{eq:ArA}-\ref{eq:Arn}) is defined according to the ability of the model to represent the non-linear dependence of the stress versus the strain and its generalization.
The values $\ln\!A_i$, $\alpha_i$, $n_i$, and $Q_i$ ($i=1,2,3,\cdots,m$) are the coefficients of the polynomials to determine using a regression method.
Setting $m=9$ gives the best results and the corresponding parameters are reported in Table \ref{tab:AR}.
\begin{table}[h!]
\centering
\caption{Parameters' values of the Arrhenius flow law for the P20 steel}
\begin{tabular}{llll}
\hline
\multicolumn{1}{c}{$\alpha_i$} & \multicolumn{1}{c}{$Q_i~(\times 10^{-6})$} & \multicolumn{1}{c}{$\ln\!A_i$} & \multicolumn{1}{c}{$n_i$}\\
\hline
$\alpha_0=0.0407$ & $Q_0=0.467$ & $A_0=35.8092$ & $n_0=4.8217$\\
$\alpha_1=-0.5167$ & $Q_1=-0.6517$ & $A_1=-58.822$ & $n_1=3.2814$\\
$\alpha_2=6.3912$ & $Q_2=7.6084$ & $A_2=740.3303$ & $n_2=71.5963$\\
$\alpha_3=-47.3364$ & $Q_3=-48.016$ & $A_3=-5.0493\times 10^{3}$ & $n_3=-1.9562\times 10^{3}$\\
$\alpha_4=220.0014$ & $Q_4=66.795$ & $A_4=1.1305\times 10^{4}$ & $n_4=1.4461\times 10^{4}$\\
$\alpha_5=-654.4553$ & $Q_5=468.8898$ & $A_5=2.022\times 10^{4}$ & $n_5=-5.431\times 10^{4}$\\
$\alpha_6=1.2421\times 10^{3}$ & $Q_6=-2.3032\times 10^{3}$ & $A_6=-1.5387\times 10^{5}$ & $n_6=1.1761\times 10^{5}$\\
$\alpha_7=-1.4523\times 10^{3}$ & $Q_7=4.3707\times 10^{3}$ & $A_7=3.1798\times 10^{5}$ & $n_7=-1.4882\times 10^{5}$\\
$\alpha_8=952.0619$ & $Q_8=-3.9394\times 10^{3}$ & $A_8=-2.9725\times 10^{5}$ & $n_8=1.0239\times 10^{5}$\\
$\alpha_9=-267.4994$ & $Q_9=1.397\times 10^{3}$ & $A_9=1.0759\times 10^{5}$ & $n_9=-2.9621\times 10^{4}$\\
\hline
\label{tab:AR}
\end{tabular}
\end{table}
This modified form of the Arrhenius behavior law allows for accurate and reliable prediction over a wide range of temperatures and strain rates.
Equation (\ref{eq:ArStress}) is finally used to compute the flow stress $\sigma^y$ from the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$:
\begin{equation}
\sigma^y = \frac{1}{\alpha(\varepsilon)} \ln\left\{\left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{1}{n(\varepsilon)}} + \left[1 + \left(\frac{\mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}}{A(\varepsilon)}\right)^{\frac{2}{n(\varepsilon)}}\right]^{\frac{1}{2}}\right\}
\label{eq:ArStress}
\end{equation}

Figure \ref{fig:CompExp-AR-6} shows the comparison of the values predicted by the Arrhenius model and the experimental values.
The difference between the experimental and predicted values is small.
But for the strain rate $\mdot\varepsilon = 0.01~\ps$ and for the two low temperature values, the AR model is not able to predict the softening.
For the AR model, $\AARE=3.56~\%$ and $\RMSE=2.18~\text{MPa}$.

\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExp-AR-6}
\caption{Comparison between the experimental and predicted flow stresses by AR model}
\label{fig:CompExp-AR-6}
\end{figure}

@@

The PTM model \cite{TizeMha-2022} is a generalized formulation of the MZA model presented in Section \ref{sec:MZA}.
When establishing its formulation, the main shortcomings of the MZA model were taken into account, in order to make the PTM model flexible for any type of material studied because there is no need for a limited number of parameters as in the MZA model.
Its construction is based on the use of polynomial functions as in the AR model.
Thus, the intrinsic functions of the model, of polynomial type, allow to adjust the model according to the degree selected for each of the 4 constituent polynomials, which provides a good fit for each function.
The equation describing the PTM model is therefore given by :
\begin{equation}
\label{eq:PTM-model}
\sigma^y = \left(\sum_{i=0}^{q}{A_i\varepsilon^{p^i}}\right) \exp\left[\left(\sum_{j=0}^{r}{B_j\varepsilon^{p^j}}\right)\left(T-T_0\right) + \left(\sum_{k=0}^{s}\left(\sum_{l=0}^{t}{C_k^l\varepsilon^{p^l}} \right)\left(T-T_0\right)^k \right)\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)\right]
\end{equation}
where $A_i, B_j, C_k^l$ are the parameters (Table \ref{tab:PTM}) of the model to be identified using the procedure proposed in  \cite{TizeMha-2022}.
Quantities $q$, $r$, $s$ and $t$ define the degree of the polynomials used to describe the behavior of the material.
The larger these quantities are, the more parameters need to be identified for the PTM model.
The determination of the parameters of this model are calculated thanks to the LMFIT Python library \cite{Newville-2016} and for more details about this model  we invite the reader to read our previous work \cite{TizeMha-2022}.
Thus, all the parameters of this model are calculated with $q=5$, $r=5$, $s=1$ and $t=5$.

Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:CompExp-PTM-6}.
The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$ the prediction in not quite good.
The deviation between the predicted values and the experimental values for other strain rates is relatively good.
For the PTM model, $\AARE=4.79~\%$ and $\RMSE=4.59~\text{MPa}$ this shows an overall worse performance than the AR model.
